RegressionPvNP

### 2017-07-05 RegressionPvNP.Rmd
...

>>>>

#### Correlations

```{r echo=F, message=F, warning=F}
library(Hmisc)

flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut],
    p = pmat[ut]
    )
}

head(dysplasia.df)
rc = rcorr(dysplasia.df)
rc = flattenCorrMatrix(rc$r, rc$P)

rc = subset(rc, row %in% rownames(coefs[[select.alpha]]) | column %in% rownames(coefs[[select.alpha]]))
rc = subset(rc, p < 0.05)

nrow(rc)
head(rc)

pos = do.call(rbind.data.frame, strsplit(as.character(rc$column), ':|-'))
colnames(pos) = c('col.chr','col.start','col.end')
pos[] = lapply(pos[], function(x) as.numeric(as.character(x)))
rc = cbind(pos, rc)

pos = do.call(rbind.data.frame, strsplit(as.character(rc$row), ':|-'))
colnames(pos) = c('row.chr','row.start','row.end')
pos[] = lapply(pos[], function(x) as.numeric(as.character(x)))
rc = cbind(pos, rc)

rc$r.coef = as.integer(rc$row %in% rownames(coefs[[select.alpha]]))

head(rc)

rc = subset(rc, cor >= 0.5)

rc = arrange(rc, row.chr, col.chr, row.start, col.start)
head(rc)

#rc[sort(c(which(rc$r.coef == 1), which(rc$r.coef == 1)+1)),]

rc1  = subset(rc, row.chr == 16 & col.chr == 16)

rc1 = transform(rc1, row=reorder(row, -row.start) ) 
rc1 = transform(rc1, column=reorder(column, col.start) )

subset(rc1, column == '16:85599240-90354752' | row == '16:85599240-90354752')

head(rc1)

ggplot(rc1, aes(column, row, fill=cor)) + geom_tile()  +  #scale_fill_gradient(low = "white", high = "red") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

## closer regions are more liklye to be correlated
cor.test(rc1$col.start - rc1$row.end , rc1$cor)
